\chapter*{Executive summary}

\noindent
\begin{longtable}{|p{\dimexpr \linewidth-2\tabcolsep-2\arrayrulewidth}|}
\hline%------------------------------------------------------------
\sumheading  Title of Project \\
\hline%------------------------------------------------------------
 Raspberry Pi Laparoscope \\[1ex]

\hline%------------------------------------------------------------
\sumheading  Objectives \\
\hline%------------------------------------------------------------
 The objective of this project is to design, program, build and test a low-cost laparoscope. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What is current practice and what are its limitations? \\
\hline%------------------------------------------------------------
 Current laparoscope use in industry is expensive and not feasible to purchase for training and prototy testing of new laparoscopic medical robots. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What is new in this project? \\
\hline%------------------------------------------------------------
 For this project, instead of specialized lenses and camera modules, off-shelf products will be utilized to develop the product. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  If the project is successful, how will it make a difference? \\
\hline%------------------------------------------------------------
 If this project is successful, it can save cost when designing and prototyping new medical robots. It can be utilized for training of new surgeons trainees. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What are the risks to the project being a success? Why is it expected to be successful? \\
\hline%------------------------------------------------------------
 The main risk of this project is delayed due to unavailability of hardware components. Therefore, the ordering of products is the main priority during early stages of the project. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What contributions have/will other students made/make? \\
\hline%------------------------------------------------------------
 Another student is performing the same project is me, thus notes and methods will be compared. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  Which aspects of the project will carry on after completion and why? \\
\hline%------------------------------------------------------------
 The developed laparoscope will be utilized in future projects, where medical robots will be devoloped. The test station will also be utilized in testing future laparoscope designs. \\[1ex]

\hline%------------------------------------------------------------
\sumheading  What arrangements have been/will be made to expedite continuation? \\
\hline%------------------------------------------------------------
To prevent delays, safety measures have been taken to prioritise the ordering of important hardware components.\\[1ex]

\hline%------------------------------------------------------------
\end{longtable}



