\chapter{GA Self Assessment}


\begin{longtable}{|p{0.45\textwidth}|p{0.45\textwidth}|}

\hline
\textbf{Graduate Attribute} & \textbf{How it will be satisfied} \\
\hline
\endfirsthead

\hline
\textbf{Graduate Attribute (continued)} & \textbf{How it will be satisfied (continued)} \\
\hline
\endhead

\hline
\multicolumn{2}{r|}{\textit{Continued on next page...}} \\
\hline
\endfoot

% ---- LAST PAGE FOOTER ----
\endlastfoot

% ---- GA 1 ----
\textbf{GA 1 - Problem solving:} Identify, formulate, research literature and analyse complex engineering problems reaching substantiated conclusions using first principles of mathematics, natural sciences and engineering sciences with holistic considerations for sustainable development. 
& 
This GA will be satisfied during the literature review, design specification reports, concept generation reports and the detail design reports, including drawing packs. \\
\hline

% ---- GA 2 ----
\textbf{GA 2 - Application of scientific and engineering knowledge:} 
Apply knowledge of mathematics, natural science, computing and engineering fundamentals, and an engineering specialisation to develop solutions to complex engineering problems. 
& 
GA 2 will be satisfied during sections where component specification and selection will be conducted. It will also be satisfied during detail design sections where analysis of the design will be performed. \\
\hline

% ---- GA 3 ----
\textbf{GA 3 - Engineering Design:} Design creative solutions for complex engineering problems and design systems, components or processes to meet identified needs.
& 
This GA will be satisfied by following the workplan and planned schedule of the project. It will also be satisfied during component selection, detail design process and the evaluation of the developed product. \\
\hline

% ---- GA 5 ----
\textbf{GA 5 - Use of Engineering Tools:} Demonstrate competence to create, select and apply and recognise limitations of appropriate techniques, resources and modern engineering and IT tools, including prediction and modelling, to complex engineering problems.
& 
GA 5 will be satisfied during the detail design of the project. It will also be satisfied during the implementation of the laparoscope. \\
\hline

% ---- GA 6 ----
\textbf{GA 6 - Professional and technical communication:} Demonstrate competence to communicate effectively and inclusively on complex engineering activities, both orally and in writing, with the engineering community and society at large, taking into account cultural, language, and learning differences.
& 
GA 6 will be satisfied during the documentation of the project, including the progress and final report. It will also be satisfied during the weekly meetings, progress meeting and final presentation. \\
\hline

% ---- GA 8 ----
\textbf{GA 8 - Individual and collaborative teamwork:} Demonstrate competence to function effectively as an individual and as a member or leader in diverse and inclusive teams, and in multi-disciplinary, face-to-face, remote and distributed settings.
& 
This GA will be satisfied during the construction of the laparoscope and testing station. It will also be satisfied during the testing stages of the laparoscope. \\
\hline

% ---- GA 9 ----
\textbf{GA 9 - Independent Learning Ability:} Demonstrate competence to engage in independent learning through well-developed learning skills.
& 
This will be satisfied during the entirety of the project, but predominantly during the literature review. \\
\hline

\caption{GA self-assessment}
\label{tab:longtable}
\end{longtable}